Equivalent Income Outcome Visualisation - Batch out

### 2024-01-10 minos/outcomes/equivalent_income_out_batch.Rmd
Last ditch scrawling effort to get some results for Vienna. Struggle

```{r}
S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'SIPHER7/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

@@

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
child.batch <- calc_age_group(child.batch)
pov.batch <- calc_age_group(pov.batch)
```

@@

base.batch <- calc_income_quintile(base.batch)
wage.batch <- calc_income_quintile(wage.batch)
energy.batch <- calc_income_quintile(energy.batch)
child.batch <- calc_income_quintile(child.batch)
pov.batch <- calc_income_quintile(pov.batch)
```

@@

```{r}
base.bat.sub <- base.batch %>%
  select(pidp, time, run_id, hh_income, weight) %>%
  group_by(run_id, time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))

base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)

big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]

base.bat.sub12 <- base.bat.sub %>%
  filter(run_id != big.run.id)

ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Household Income: Individual Runs')

ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Household Income: Individual Runs')

ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
  geom_smooth() +
  labs(title = 'Household Income: Smoothed mean')

ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
  geom_smooth() +
  labs(title = 'Household Income: Smoothed mean')

base.bat.sub2 <- base.bat.sub %>%
  group_by(time) %>%
  summarise(var = mean(hh_income),
         min = min(hh_income),
         max = max(hh_income))

base.bat.sub22 <- base.bat.sub12 %>%
  group_by(time) %>%
  summarise(var = mean(hh_income),
         min = min(hh_income),
         max = max(hh_income))

ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Household Income: Min - Max')

ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Household Income: Min - Max')
```

@@

```{r}
base.bat.sub <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(run_id, time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))

base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)

big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]

base.bat.sub12 <- base.bat.sub %>%
  filter(run_id != big.run.id)

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Equivalent Income: Individual Runs')

ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Equivalent Income: Individual Runs')

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
  geom_smooth() +
  labs(title = 'Equivalent Income: Smoothed mean')

ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
  geom_smooth() +
  labs(title = 'Equivalent Income: Smoothed mean')

base.bat.sub2 <- base.bat.sub %>%
  group_by(time) %>%
  summarise(var = mean(equivalent_income),
         min = min(equivalent_income),
         max = max(equivalent_income))

base.bat.sub22 <- base.bat.sub12 %>%
  group_by(time) %>%
  summarise(var = mean(equivalent_income),
         min = min(equivalent_income),
         max = max(equivalent_income))

ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Equivalent Income: Min - Max')

ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Equivalent Income: Min - Max')
```

@@

```{r}
equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))

@@

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
    xlab('Year') +
    ylab('Equivalent Income (£)')

@@

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_fullpop_batch(base.batch, pov.batch, 'PovertyChild')
```

```{r}
base.subset <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'Baseline')

wage.subset <- wage.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'LivingWage')

energy.subset <- energy.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'EnergyCrisis')

child.subset <- child.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'AllChild')

pov.subset <- pov.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'PovertyChild')

all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

@@

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))

@@

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
equivalent_income_comparison_treated_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
```

@@

income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_change_batch(base.batch, child.batch, 'All Child')
income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
equivinc_change_batch(base.batch, child.batch, 'All Child')
equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
```

@@

income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child')
income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
```

@@

```{r}
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

@@

```{r}
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
```

@@

```{r}
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
```

>>>>

```{r}
S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'TEST_BATCH/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2024, var.list = S7.var.list, verbose=TRUE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2024, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
#energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2024, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
#pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

@@

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
#energy.batch <- calc_age_group(energy.batch)
child.batch <- calc_age_group(child.batch)
#pov.batch <- calc_age_group(pov.batch)
```

@@

base.batch <- calc_income_quintile(base.batch)
wage.batch <- calc_income_quintile(wage.batch)
#energy.batch <- calc_income_quintile(energy.batch)
child.batch <- calc_income_quintile(child.batch)
#pov.batch <- calc_income_quintile(pov.batch)
```

@@

```{r}
# base.bat.sub <- base.batch %>%
#   select(pidp, time, run_id, hh_income, weight) %>%
#   group_by(run_id, time) %>%
#   summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))
# 
# base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
# 
# big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]
# 
# base.bat.sub12 <- base.bat.sub %>%
#   filter(run_id != big.run.id)
# 
# ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
#   geom_line() +
#   labs(title = 'Household Income: Individual Runs')
# 
# ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
#   geom_line() +
#   labs(title = 'Household Income: Individual Runs')
# 
# ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
#   geom_smooth() +
#   labs(title = 'Household Income: Smoothed mean')
# 
# ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
#   geom_smooth() +
#   labs(title = 'Household Income: Smoothed mean')
# 
# base.bat.sub2 <- base.bat.sub %>%
#   group_by(time) %>%
#   summarise(var = mean(hh_income),
#          min = min(hh_income),
#          max = max(hh_income))
# 
# base.bat.sub22 <- base.bat.sub12 %>%
#   group_by(time) %>%
#   summarise(var = mean(hh_income),
#          min = min(hh_income),
#          max = max(hh_income))
# 
# ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
#   geom_line() +
#   geom_ribbon(aes(ymin = min, ymax = max), 
#                 alpha = 0.1,
#                 linetype = 'dashed') +
#   labs(title = 'Household Income: Min - Max')
# 
# ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
#   geom_line() +
#   geom_ribbon(aes(ymin = min, ymax = max), 
#                 alpha = 0.1,
#                 linetype = 'dashed') +
#   labs(title = 'Household Income: Min - Max')
```

@@

```{r}
# base.bat.sub <- base.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(run_id, time) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))
# 
# base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)
# 
# big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]
# 
# base.bat.sub12 <- base.bat.sub %>%
#   filter(run_id != big.run.id)
# 
# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
#   geom_line() +
#   labs(title = 'Equivalent Income: Individual Runs')
# 
# ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
#   geom_line() +
#   labs(title = 'Equivalent Income: Individual Runs')
# 
# ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
#   geom_smooth() +
#   labs(title = 'Equivalent Income: Smoothed mean')
# 
# ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
#   geom_smooth() +
#   labs(title = 'Equivalent Income: Smoothed mean')
# 
# base.bat.sub2 <- base.bat.sub %>%
#   group_by(time) %>%
#   summarise(var = mean(equivalent_income),
#          min = min(equivalent_income),
#          max = max(equivalent_income))
# 
# base.bat.sub22 <- base.bat.sub12 %>%
#   group_by(time) %>%
#   summarise(var = mean(equivalent_income),
#          min = min(equivalent_income),
#          max = max(equivalent_income))
# 
# ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
#   geom_line() +
#   geom_ribbon(aes(ymin = min, ymax = max), 
#                 alpha = 0.1,
#                 linetype = 'dashed') +
#   labs(title = 'Equivalent Income: Min - Max')
# 
# ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
#   geom_line() +
#   geom_ribbon(aes(ymin = min, ymax = max), 
#                 alpha = 0.1,
#                 linetype = 'dashed') +
#   labs(title = 'Equivalent Income: Min - Max')
```

@@

```{r}
equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = mean(equivalent_income))
  int.subset <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income =  mean(equivalent_income))

@@

  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name)) +
    xlab('Year') +
    ylab('Equivalent Income (£)')

@@

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'ChildBenefit')
```

```{r}
# base.subset <- base.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'Baseline')
# 
# wage.subset <- wage.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'LivingWage')
# 
# # energy.subset <- energy.batch %>%
# #   select(pidp, time, run_id, equivalent_income, weight) %>%
# #   group_by(time, run_id) %>%
# #   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
# #   mutate(scenario = 'EnergyCrisis')
# 
# child.subset <- child.batch %>%
#   select(pidp, time, run_id, equivalent_income, weight) %>%
#   group_by(time, run_id) %>%
#   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
#   mutate(scenario = 'AllChild')
# 
# # pov.subset <- pov.batch %>%
# #   select(pidp, time, run_id, equivalent_income, weight) %>%
# #   group_by(time, run_id) %>%
# #   summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
# #   mutate(scenario = 'PovertyChild')
# 
# all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
# all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))
# 
# ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
#   geom_smooth() +
#   labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
#   xlab('Year') +
#   ylab('Equivalent Income (£)')
```

@@

  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario, run_id) %>%
    summarise(equivalent_income =  mean(equivalent_income))

@@

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
#equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
equivalent_income_comparison_treated_batch(base.batch, child.batch, 'ChildBenefit')
#equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
```

@@

#income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_change_batch(base.batch, child.batch, 'All Child')
#income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

#equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
equivinc_change_batch(base.batch, child.batch, 'All Child')
#equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

# equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
# equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
# equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
# equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
```

@@

#income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child')
#income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
```

@@

# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
# income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
```

@@

```{r}
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
# equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')
# 
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
# S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

@@

```{r}
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
# equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
# 
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
# S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
```

@@

```{r}
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
# equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')
# 
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
# S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
```
